### 2019-11-04 peer-review/review-response.Rmd

## Authors' response to Editorial Requests

GENERAL

- In both the abstract and the main text please define all abbreviations at first use (e.g. UK; gradient boosting method – is this GBM?; 95%CI – is CI confidence interval? Credible interval?; MNAR in the discussion – is this missing not at random mechanism?). For Tables and Figures, please define all abbreviations used in a footnote below the Figure or Table.

*We have reviewed all abbreviations and added definitions where missing. Tables and footers have been checked for abbreviations without explanations and these have been added when missing. We added missing explanations for the abbreviations in the abstract*

@@

- If possible, please use square brackets for the references with the punctuation following the reference.

*We have moved to using square brackets and moved to punctuation following the reference.*

@@

- Tables should not have any empty cells as design element or because information is not available ('NA' (subsequently defined as not available or not applicable) can be used for example).

*We have re-formatted the tables to limit empty cells while still clearly imparting The correct information. Where fields do not contain data we have indicated this with a dash (-) and only used NA for missing data in the conventional sense. Having this information in a single table allows for easier between model comparisons which we feel is essential to the presentation of our results. We have also included all results in csv form for readers who wish to use our results programmatically. We have clarified this in the data availability section. However, we are happy to alter the table design if we can preserve the clarity of the results presentation.*

@@

- For all Figure and Table titles, when possible, please indicate at the end of the title, the geographical area, period and total number of items covered by the illustration. E.g. Table 1: Summary of relevance and eligibility criteria for each cohort, United Kingdom, 2000-2010 (n = xxx individuals)

*We have added location and temporal information to all tables/figures. As this was a retrospective whole population based study based on surveillance data, sample sizes are not useful in this instance (as they are the whole population meeting the cohort critiera which is age based).*

@@

*We have added an aim section that includes the aim of the paper and the study type. We have also made the required cuts to the abstract in order to keep within the word limit.*

METHODS

Data sources 
- Does the Labour Force Survey record only the number of adults of working age (employed or unemployed) in the country, or does it record more people than these (e.g. their family members such as children)? Please describe the population and demographics recorded in the Labour Force Survey in more detail.

*The LFS is the largest household study in the UK. Whilst it is used primarily to estimate unemployment rates it is also designed to be used by local governments etc. to understand the structure of their population. It therefore provides some of the best available yearly population estimates that are stratified by ethnicity, UK birth status, and age. A caveat to this is that it may not capture the older adult poplulation well. However, this was not relevant to this study as those individuals were not directed impacted by the change in policy. We have added these additional detials to the manuscript.*

@@

2.	Paragraph 2. Not clear whether the LFS which reports "employment circumstances" of the UK population reports also data in children, who are not employed. We assume the answer is yes which should be probably clarified.

*We have added additional details to this section. Please see the responses to the editors comments for an expanded discussion of the LFS.*

3.	Definition of cohorts. Not totally clear to me. Example for comparison cohort 2: a child born in 2000 and who is diagnosed with TB at 2 years old (2002): the vaccination programme in 2002 is universal not targeted, as seen in Table 1. Maybe further clarify this crucial point.

*We agree that this is somewhat difficult to interpret as the underlying cohort structure is complex. The cohorts are first identified based on age. Eligibility is then used to indicate if a given cohort was enrolled on the universal or targeted  programme. This gives a cohort who were enrolled and a comparison cohort who were not (resulting in a binary outcome). We have added additional detail outlining this to the paper.*

@@

This is a key point that should be reviewed by a statistician; I do not feel confident on giving my opinion on this.

Results

1.	No comments, except that I find some parts of the results difficult to understand for a "common" public health professional" with no deep knowledge on statistics and modelling methods.

*We have tried to make the results section readable but happy to take suggestions on which sections in particular to improve.*

@@

3.	No figures of BCG vaccination coverage trends in targeted groups are given (except the 68% mentioned in the Discussion). This determines to a large extent the impact of vaccination. A brief description of this could be given here, or in Introduction.

*We agree that vaccination coverage impacts the success/failure of vaccination programmes. Unfortunately, coverage estimates for the targeted vaccination programme are of very poor quality. This was part of the motivation for using a population based approach that looked at overall incidence rates and hence did not need to account for vaccination coverage. We agree that understanding coverage in targeted populations should be a focus for further work in this area.*

4.	BCG has an impact mainly in severe forms of TB, and prevents about 50% of pulmonary TB in children. But children, to my knowledge, do not frequently transmit TB. So BCG has rather poor effect on TB transmission. The authors speak in their discussion on indirect effects and ongoing transmission. Is this really the case with BCG and TB?

*This is an interesting point and the motivator for some of our current research. Whilst the reviewer is correct that children are less likely to be smear-positive this is not the case for adults. This means that school-age vaccination may lead to fewer overall cases in children than direct vaccination of children once onwards transmission has been accounted for due to increased protection from TB as young adults. This depends on the level of TB transmission in the population and therefore may not be relevant in the UK where transmission is generally thought to be low. For areas where the BCG mainly impacts severe forms of TB only we agree that direct vaccination of children is more clearly beneficical. However, there is good evidence of effectiveness for the BCG when given later in life in the UK meaning that there is likely an incidence rate thresold at which school-age vaccination becomes more protective.*

@@

## Authors' response to Reviewer #3:

This study is of high relevance, not just for the England, but for the global tuberculosis community: The UK (England and Wales notably) had been one of the few countries with a universal vaccination of adolescents and a clinical trial demonstrating high efficacy for at least 20 years in the age vaccinated groups and beyond to include young adults during follow-up.

From the switch from universal adolescent vaccination to selective (largely the descendant newborn of foreign-born ancestors) one would thus hypothetically expect an increase in the incidence rate among the former and a decrease in the incidence rate among the latter (among the respective cohorts in both groups), if confounding resulting from secular trends could be properly controlled for. This study aimed to do precisely that.

*Thank you for this detailed and helpful review. We hope that the findings from this study should be relevant to the global TB community. We particularly appreciate your suggestions for improving the discussion of the approach used.*

### 2019-11-05 README.Rmd
finalised reviewer responses

In 2005, England changed from universal Bacillus Calmette–Guérin (BCG) vaccination of school-age children to targeted BCG vaccination of high-risk neonates.

@@

Estimate the impact of the 2005 change in BCG policy on incidence rates in the targeted populations of England using an observational study.

@@

We combined notifications from the Enhanced Tuberculosis Surveillance system, with demographic data from the Labour Force Survey to construct retrospective cohorts relevant to both the universal, and targeted vaccination between Jan 1, 2000 and Dec 31, 2010. We then estimated incidence rates over a 5 year follow-up period and used regression modelling to estimate the impact of the change in policy on TB.

>>>>

In 2005 in England, universal Bacillus Calmette–Guérin (BCG) vaccination of school-age children was replaced by targeted BCG vaccination of high-risk neonates.

@@

Estimate the impact of the 2005 change in BCG policy on tuberculosis incidence rates in England.

@@

We conducted an observational study by combining notifications from the Enhanced Tuberculosis Surveillance system, with demographic data from the Labour Force Survey to construct retrospective cohorts relevant to both the universal, and targeted vaccination between Jan 1, 2000 and Dec 31, 2010. We then estimated incidence rates over a 5 year follow-up period and used regression modelling to estimate the impact of the change in policy on TB.
